\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.75]{geometry}

\firstname{Salvador}
\familyname{Hernández López}
\title{Full Stack Developer} 
% \address{San Pab and number}{postcode city} 
\mobile{+52~(351)~281~3013} 
% \phone{+2~(345)~678~901} 
% \fax{+3~(456)~789~012} 
\email{chavatloz@gmail.com} 
% \homepage{chavati.github.io/Portafolio/} 
\extrainfo{This document was created using \LaTeX}


\begin{document}

\makecvtitle

\section{Areas of Knowledge}
\cvitem{React}{I fully know how to use class components, functional components, hooks, contex , reducers and Redux, using modern ecmascript syntax like React documetation suggest. I've used material UI to the user experience of the projects}
\cvitem{Vue}{I've developed Vue applications using tools as Vuex, boostrap-vue, UI vue tools.}
\cvitem{Angular}{I master using the components of this framework and I always take advantage of the angular materials to have good UI results.}
\cvitem{Lambda functions}{I've worked with AWS lambda functions and SAM to work locally with them.}
\cvitem{Serverless}{I've worked with the framework Serverless to deploy AWS lambda functions, and some tools to work with them locally.}
\cvitem{Javascript}{Due to I've used framerworks like React, Vue and Angular I've mastered the Javascript language.}
\cvitem{Typescript}{I've used typescript in order to make more robust the code and to have a better experience coding.}
\cvitem{NodeJs}{I used to develop web apps using NodeJS Express and Jade. But, nowadays I’ve tended to make API rests in order to make MEAN/MERN/MEVN stack apps.}
\cvitem{Ruby on Rails}{I've manteinig a project on Ruby and Rails coding API endpoints and unit test.}
\cvitem{Laravel}{I've created projects with Laravel framework using the MVC Laravel tools and the testing tools.}
\cvitem{Contentful}{I've consumed the contentful API from nodejs and ruby on rails projects, also I've created migrations, content models and content types, I've created tranformer to handle the contentful API response and return the data in JSON API standard.}
\cvitem{Algolia}{I've consumed algolia in a React project, I've created a custom hook to consume the algolia API and return the data in a JSON API standard.}
\cvitem{Docker}{In order to develop and deploy some projects I've created containers and images using docker and docker-compose.}
\cvitem{Lua}{Since I'm a neovim user, I've created my own setup from scratch using lua as programming language. Also I'm a enthusiast of the neovim plugins I usually read code of these plugins in github.}
\cvitem{C++}{C++ for me it's a hobby, I've created some algorithms of computer science and I've read some books about this language.}
\cvitem{Databases}{I start designing the database and then I implement them in MySQL , PosgresDB, MariaDB or SQLServer.}
\cvitem{Java}{I have a lot of experience coding in Java since I’ve worked with it for a long time. I know how to make either CLI apps, GUI apps and web apps.}

\section{Tools}
\cvitem{Neovim}{In order to improve my efficiency coding, I write my code in neovim with my own setup.}
\cvitem{Copilot}{I use Github Copilot in order to be more efficient and save time in the code time.}
\cvitem{Github actions}{I've used Github actions to deploy my projects in AWS lambda functions, run unit test and lint the code.}
\cvitem{Visual Studio Code}{I usually use Vscode on pair programing sessions using LiveShare pluggin.}
\cvitem{Git}{I've worked with Git servers like Github, Gitlab, Bitbucket using Gitflow as git workflow.}
\cvitem{Swagger}{I've used swagger in order to check how the API going to answer and how I should map the data in front end.}
\cvitem{Storybook}{In order to isolate components and work with them easily, I've worked with storybook.}
\cvitem{Jira}{I've used the Jira board joined with bitbucket to verify tickets and work the kanban / scrum with the team.}
\cvitem{Slack}{Much of the time I've communicated with the team with this tool.}
\cvitem{Google Meet}{The meetings to scrum or just to ask or resolve quick questions usually I use Google meets.}

\section{Professional Experience}
\cventry{2021--Present}{Full stack developer}{JibJab}{}{}{}
\cvitem{}{Working at JibJab I've created features and components on the web app, working on the React frontend with tools like React Router, MaterialUI, JSS, Redux, React, Algolia React components, React recurly, and Storybook. On the backend side I've worked with a REST API made it in ruby on rails and using JSON API specification and I've maintained AWS lambda functions using Serveless framework, I've mantained a contentful proxy API where I used the nodejs contentful API and others contentful tools, using typescript.}
\cventry{2018--2021}{Web developer}{The Software Artisans}{}{}{}
\cvitem{}{Under the period on TSA I've developed web solutions using differents tools for example NodeJS, Laravel, Angular, VueJS etc. and I've trained new people in TSA.}

\cventry{2020}{Web developer}{XML Team Solutions, LLC}{}{}{}
\cvitem{}{I've developed a CRUD web application using Laravel and docker.}
\cventry{2017-2018}{Developer and tester}{Instituto Tecnológico de Estudios Superiores de Zamora}{}{}{}
\cvitem{}{I've created multiples modules to CRUD web applications using PHP}


\nocite{*}
\bibliographystyle{plain}
\bibliography{publications} % a bibtex file containing the list of publications

\end{document}

